---
title: "LMwithPred"
author: "Lelainy Saavedra"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Introduction  
This is a linear model with prediction problems. It predicts strenght scores using data from the following website.    

$H_O$: There is NO difference between these models, they all work great.  
$H_A$: There IS a difference in these models, one of them works beter than the other.  




```{r}
data <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE) 

```
```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
if(!require("rglwidget")) {install.packages("rglwidget");require("rglwidget")}
require(knitr)
require(ggplot)
```
## Graphical Results
We are going to be using a Numerical~Numerical template.

### Plot scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

```{r}
basicNN <- ggplot(data,aes(y=SIMS, x=ARM))
```
```{r}
basicNN + geom_point()+geom_smooth(method=lm)
```
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
New=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,New, interval="prediction")
```

## Model 2

```{r}
plot(SIMS~GRIP,data=data)
```


```{r}
basicNN <- ggplot(data,aes(y=SIMS, x=GRIP))
```
```{r}
basicNN + geom_point()+geom_smooth(method=lm)
```
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
New=data.frame(GRIP=94, ARM=88)
predict.lm(model.2,New,interval="predict")


```
## Model 3
  
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
New=data.frame(GRIP=94, ARM=88)
predict.lm(model.3,New,interval="predict")
```

```{r}
anova(model.3,model.2)
```
As we can see by this Anova chart, there is a difference in the models because model 1 is higher than the other 2 models
## Conclusion

