---
title: "LMwithPred"
author: "Lelainy Saavedra"
date: "10/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Introduction  
This is a linear model with prediction problems. It predicts strenght scores using data from the following website.    

$H_O$: There is NO difference between these models, they all work great.  
$H_A$: There IS a difference in these models, one of them works beter than the other.  




```{r}
data <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE) 

```
```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
if(!require("rglwidget")) {install.packages("rglwidget");require("rglwidget")}
require(knitr)
require(ggplot)
```
## Graphical Results  
We are going to be using a Numerical~Numerical template.  

### Plot scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

This scatter plot shows us the physical strenght of some people, we are trying to analyze which chart is better for the type of information we are trying to find, we input the ARM and the SIMS data.  
```{r}
basicNN <- ggplot(data,aes(y=SIMS, x=ARM))
```
```{r}
basicNN + geom_point()+geom_smooth(method=lm)
```
  
In this gg plot, we wanted to see a more complex view of the results.   

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
New=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,New, interval="prediction")
```
We used the predict option and found our  Adjusted R-squared to be:  0.467  
## Model 2

```{r}
plot(SIMS~GRIP,data=data)
```


```{r}
basicNN <- ggplot(data,aes(y=SIMS, x=GRIP))
```
```{r}
basicNN + geom_point()+geom_smooth(method=lm)
```
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
New=data.frame(GRIP=94, ARM=88)
predict.lm(model.2,New,interval="predict")


```

For Model 2, our adjusted Rsquare was of:0.4053, which makes it less than the first model.  
## Model 3
  
```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
New=data.frame(GRIP=94, ARM=88)
predict.lm(model.3,New,interval="predict")
```


```{r}
anova(model.3,model.2)
```
In this last Analysis we have added Model 1 and Model 3,using anova. The value that it gives us is of 1.495e-09. By adding these results we conclude that the first model is a better model of the three because is Rsquare is more than 1.  

## Conclusion    
We reject the Null Hypothesis because There IS a difference in these regression   models, Model 1 Rsquare value is   0.467, Model 2 Rsquare value 0.4053,and for model 3 where the first two were combined gave us an Rsquare value of 1.495e-09. since model 1 is the highest that means that model 1 works better than the other two, the Rsquare can never be bigger than 1, but the model with highest adjusted R square is always best.  

